Type-Safe Modular Parsing

### 2016-10-19 paper/sections/CaseStudy.tex
Some text

When composing the calculus from components, the \lstinline{Alg} and \lstinline{Print} can be easily combined by Scala’s \lstinline{extends...with} keywords as shown in the code. For \lstinline{Parser}, the subtyping constraint for the explicit self-reference should satisfy all the requirement of the parsers it extends from. \huang{Talk about | here?}

@@

Except building a component by extending an existing one, here we have another extension which is adding a new sort of syntax. It has been discussed in section \ref{subsec:openrecursion}. In this example, originally \lstinline{VarApp} has only one sort of syntax which is expressions, and then \lstinline{Typed} introduces types to the syntax. We add an extra type parameter \lstinline{T} for it, so that it is able to be distinguished. The \lstinline{Parser} also requires the self-reference to have a field \lstinline{pT} for parsing types, which is represented by the subtyping constraint. With this support, the \lstinline{pTypedT} function parses arrow types using \lstinline{pT}.

>>>>

When composing the calculus from components, all the fields can be easily combined by Scala’s \lstinline{extends...with} keywords as shown in the code. For \lstinline{Parser}, the subtyping constraint for the explicit self-reference should satisfy all the requirement of the parsers it extends from. \huang{Talk about | here?}

@@

Except building a component by extending an existing one, here we have another extension which is adding a new sort of syntax. It has been discussed in section \ref{subsec:openrecursion}. In this example, originally \lstinline{VarApp} has only one sort of syntax which is expressions, and then \lstinline{Typed} introduces types to the syntax. We add an extra type parameter \lstinline{T} for it, so that it is able to be distinguished. The \lstinline{Parser} also requires the self-reference to have a field \lstinline{pT} for parsing types, which is represented by the subtyping constraint. With this support, the \lstinline{pTypedT} function parses arrow types using \lstinline{pT}. Another point worth mentioning is that we use a private local function \lstinline{pAbsE} here for parsing the typed lambda abstraction case, and we can directly combine it with the inherited \lstinline{pVarApp} to obtain our parsing function of expressions.

Since calculi and components have the similar signature, each calculus can also be extended and reused directly. Our last example shows how to build calculus \lstinline{FullRef} from extending \lstinline{FullSimple}, another calculus.

\begin{lstlisting}
object FullRef {
  trait Alg[E, T] extends FullSimple.Alg[E, T] with TopBot.Alg[T] with Ref.Alg[E, T]
  trait Print extends Alg[String, String] with FullSimple.Print with TopBot.Print with Ref.Print
  trait Parser[E, T, L <: {val pE : PackratParser[E]; val pT : PackratParser[T]}] extends FullSimple.Parser[E, T, L] with TopBot.Parser[T, L] with Ref.Parser[E, T, L] {
    val pFullRefE = pFullSimpleE | pRefE
    val pFullRefT = pFullSimpleT | pRefT | pTopBotT
  }
}
\end{lstlisting}

Using our modular parsing library, dividing the syntax into small pieces and bind them with corresponding parsers to form reusable language component is convenient. From the dependency graph we know that the common components such as \lstinline{VarApp} are reused in lots of calculi. Such reuse could shorten the codes considerably. We will show this advantage and exam the possible performance penalty in a quantitative way in the next section.
